Board games group recomendation using metadata

### 2024-12-09 paper v2/paper v2.tex
feat: referencias paper
chore: additional and corrected references

Board games have been a popular form of entertainment for centuries, and their popularity has only increased in recent years. Even as digital games have become more prevalent, board games have remained a favorite pastime for many people, and the market for board games has grown significantly giving rise to plataforms such as Board Game Geek (BGG). This website is a popular platform for board game enthusiasts, where users can rate and review games, as well as access information about them.

@@

This plataform has a vast amount of data that has been used in the past to create recommendation systems. For example, 
github user richengo \cite{richengo2024} proposed a recommendation system for board games based on user ratings, using a collaborative filtering approach. However, this approach does not take into account the characteristics of many of the games, that are supposed to be played in groups. As such, we propose a group recommendation system to make recommendations tailored to groups of players.

Another example of group recommendation systems is the work of %\cite{DBLP:journals/corr/abs-2006-07053}
, who proposed a group recommendation system for tourism and movies\footnote{This work is hosted on a github repo and is intended to be used as a basic tutorial.}.
This system uses regular clustering algorithms to group users based on their ratings, such as user k-nearest, item k-nearest and support vector decomposition, and then recommends movies and touristic locations based on the preferences of the group.

@@

The dataset that will be used for this project has 10 different files, each one tith different information about board games. The main file is \texttt{user\_ratings.csv}, which contains 19 million rows. Due to the limited processing power of Google Collab and our own local machines, we will use a reduced set of items and users for this work. The other files are:

@@

Citations within the text should include the authors' last names and
year. If the authors' names are included in the sentence, place only
the year in parentheses, for example when referencing Arthur Samuel's
pioneering work \yrcite{Samuel59}. Otherwise place the entire
reference in parentheses with the authors and year separated by a
comma \cite{Samuel59}. List multiple references separated by
semicolons \cite{kearns89,Samuel59,mitchell80}. Use the `et~al.'
construct only for citations with three or more authors or after
listing all authors to a publication in an earlier reference \cite{MachineLearningI}.

Authors should cite their own work in the third person
in the initial version of their paper submitted for blind review.
Please refer to Section~\ref{author info} for detailed instructions on how to
cite your own papers.

Use an unnumbered first-level section heading for the references, and use a
hanging indent style, with the first line of the reference flush against the
left margin and subsequent lines indented by 10 points. The references at the
end of this document give examples for journal articles \cite{Samuel59},
conference publications \cite{langley00}, book chapters \cite{Newell81}, books
\cite{DudaHart2nd}, edited volumes \cite{MachineLearningI}, technical reports
\cite{mitchell80}, and dissertations \cite{kearns89}.

@@

% In the unusual situation where you want a paper to appear in the
% references without citing it in the main text, use \nocite
\nocite{langley00}

\bibliography{example_paper}
\bibliographystyle{icml2021}

>>>>

Board games have been a popular form of entertainment for centuries, and their popularity has only increased in recent years. Even as digital games have become more prevalent, board games have remained a favorite pastime for many people, and the market for board games has grown significantly giving rise to plataforms such as Board Game Geek\footnote{\cite{boardgamegeek}} (BGG). This website is a popular platform for board game enthusiasts, where users can rate and review games, as well as access information about them.

@@

This plataform has a vast amount of data that has been used in the past to create recommendation systems. For example,
github user richengo \yrcite{richengo2024} proposed a recommendation system for board games based on user ratings, using a collaborative filtering approach. However, this approach does not take into account the characteristics of many of the games, that are supposed to be played in groups. As such, we propose a group recommendation system to make recommendations tailored to groups of players.

Another example of group recommendation systems is the work of \cite{group_recommenders_repo}, who proposed a group recommendation system for tourism and movies\footnote{This work is hosted on a github repo and is intended to be used as a basic tutorial.}.
This system uses regular clustering algorithms to group users based on their ratings, such as user k-nearest, item k-nearest and support vector decomposition (SVD), and then recommends movies and touristic locations based on the preferences of the group.

@@

The dataset that will be used for this project\footnote{\cite{board_games_kaggle}}, obtained from the website kaggle, has 10 different files, each one tith different information about board games. The main file is \texttt{user\_ratings.csv}, which contains 19 million rows. Due to the limited processing power of Google Collab and our own local machines, we will use a reduced set of items and users for this work. The other files are:

@@

Citations within the text should include the authors' last names and
year. If the authors' names are included in the sentence, place only
the year in parentheses using yrcite.

@@

% In the unusual situation where you want a paper to appear in the
% references without citing it in the main text, use \nocite
% \nocite{}

\bibliography{main}
\bibliographystyle{icml2021}
